### 2017-02-28 2017mergingmerges/section/02-Processes.tex
fig 5. fused graph colours

\begin{figure}
\begin{code}
process
{ ins:    { sIn1,  sIn2 }
, outs:   { sOut1, sOut2 }
, heap:   { f = T, l = 0, v = 0, x1 = 0, x2 = 0, b1 = 0}
, label:  F0
, instrs:
\end{code}

\newcommand\annot[5]{
  \tiny ((#1,   \> \tiny \{sIn1 =      #2\}), 
                \> \tiny (#3, \> \tiny \{sIn1 =      #4, \> \tiny sIn2 =      #5\}))
}
\newcommand\icase[7]{
 \tt{#1} \> \tt{= #2} \> \tt{#3} \> \tt{[ #4 ]} \> \tt{#5} \> \tt{[ #6 ]} \> \tiny #1 \> \tiny = #7 \\
}
\newcommand\instr[5]{
 \tt{#1}\>\tt{= #2} \> \tt{#3} \> \tt{[ #4 ]} \> \> \> \tiny #1 \> \tiny = #5 \\
}
\begin{tabbing}
@  @ \=
@, F17@  \= = @case (f || (l /= v)) @
         \= @F17@ \= @[ ]     @ \= @F17@ \= @[ ]@
@   @ \= \tiny F17 \= \tiny = ((A0, \= \tiny \{sIn1 = pending\}), \= \tiny (B0, \= \tiny \{sIn1 = pending, \= \tiny sIn2 = pending\})) \kill
\> @{@ \instr{F0}{pull sIn1 b1}{F1}{}
      {\annot{A0}{none}{B0}{none}{none}}

\> @,@
\instr{F1}{jump}{F2}{v  = b1}
      {\annot{A0}{pending}{B0}{pending}{none}}
\> @,@
\instr{F2}{jump}{F3}{x1 = b1}
      {\annot{A1}{have}{B0}{pending}{none}}
\> @,@
\icase{F3}{case (f || (l /= v))}{F4}{}{F5}{}
      {\annot{A1}{have}{B1}{have}{none}}

\> @,@
\instr{F4}{push sOut1 v}{F5}{l = v, f = F}
      {\annot{A2}{have}{B1}{have}{none}}

\> @,@
\instr{F5}{jump}{F6}{}
      {\annot{A3}{have}{B1}{have}{none}}

\> @,@
\instr{F6}{pull sIn2 x2}{F7}{}
      {\annot{A0}{none}{B1}{have}{none}}
\\

\> @,@
\icase{F7}{case (x1 < x2)}{F8}{}{F16}{}
      {\annot{A0}{none}{C0}{have}{have}}

\\
\> @,@
\instr{F8}{push sOut2 x1}{F9}{}
      {\annot{A0}{none}{D0}{have}{have}}
\> @,@
\instr{F9}{drop sIn1}{F10}{}
      {\annot{A0}{none}{D1}{none}{have}}
\> @,@
\instr{F10}{pull sIn1 b1}{F11}{}
      {\annot{A0}{none}{D2}{none}{have}}
\> @,@
\instr{F11}{jump}{F11}{v = b1}
      {\annot{A0}{pending}{D2}{pending}{have}}
\> @,@
\icase{F12}{case (f || (l /= v))}{F13}{}{F14}{}
      {\annot{A1}{have}{D2}{pending}{have}}
\> @,@
\instr{F13}{push sOut1 v}{F14}{l = v, f = F}
      {\annot{A2}{have}{D2}{pending}{have}}
\> @,@
\instr{F14}{jump}{F15}{}
      {\annot{A3}{have}{D2}{pending}{have}}
\> @,@
\instr{F15}{jump}{F7}{x1 = b1}
      {\annot{A0}{none}{D2}{pending}{have}}

\\
\> @,@
\instr{F16}{push sOut2 x2}{F17}{}
      {\annot{A0}{none}{E0}{have}{have}}
\> @,@
\instr{F17}{drop sIn2}{F18}{}
      {\annot{A0}{none}{E1}{have}{have}}
\> @,@
\instr{F18}{pull sIn2}{F7}{}
      {\annot{A0}{none}{E2}{have}{none}}

@} }@
\end{tabbing}

>>>>

%%% AR: would like to highlight which machine is performing the current instruction, eg bolding "A0" when it's group moving from A0 to A1
\begin{figure}
\begin{code}
process
{ ins:    { sIn1,  sIn2 }
, outs:   { sOut1, sOut2 }
, heap:   { f = T, l = 0, v = 0, x1 = 0, x2 = 0, b1 = 0}
, label:  F0
\end{code}

\definecolor{groupc}{HTML}{308030}
\definecolor{mergec}{HTML}{800000}
\definecolor{sharec}{HTML}{000080}

\newcommand\annot[5]{
  \tiny ((#1,   \> \tiny \{sIn1 =      #2\}), 
                \> \tiny (#3, \> \tiny \{sIn1 =      #4, \> \tiny sIn2 =      #5\}))
}

\newcommand\icase[7]{
 \tt{#1} \> \tt{= #2} \> \tt{#3} \> \tt{[ #4 ]} \> \tt{#5} \> \tt{[ #6 ]} \> \tiny #1 \> \tiny = #7
}
\newcommand\instr[5]{
 \tt{#1}\>\tt{= #2} \> \tt{#3} \> \tt{[ #4 ]} \> \> \> \tiny #1 \> \tiny = #5
}

\begin{tabbing}
@  @ \=
@, F17@  \= = @case (f || (l /= v)) @
         \= @F17@ \= @[ ]     @ \= @F17@ \= @[ ]@
@   @ \= \tiny @   @F17 \= \tiny = ((A0, \= \tiny \{sIn1 = pending\}), \= \tiny (B0, \= \tiny \{sIn1 = pending, \= \tiny sIn2 = pending\})) \kill

@, instrs:@

% I have no idea how this works, but you need this particular incantation to colour the whole line in a tabbing environment.
% It's not ideal that the { and , are coloured too, but that can't be helped.
\\[0pt \color{sharec}]
\> @{@
\instr{F0}{pull sIn1 b1}{F1}{}
      {\annot{A0}{none}{B0}{none}{none}}

\\[0pt \color{groupc}]
\> @,@
\instr{F1}{jump}{F2}{v  = b1}
      {\annot{A0}{pending}{B0}{pending}{none}}

\\[0pt \color{mergec}]
\> @,@
\instr{F2}{jump}{F3}{x1 = b1}
      {\annot{A1}{have}{B0}{pending}{none}}

\\[0pt \color{groupc}]
\> @,@
\icase{F3}{case (f || (l /= v))}{F4}{}{F5}{}
      {\annot{A1}{have}{B1}{have}{none}}

\\[0pt \color{groupc}]
\> @,@
\instr{F4}{push sOut1 v}{F5}{l = v, f = F}
      {\annot{A2}{have}{B1}{have}{none}}

\\[0pt \color{groupc}]
\> @,@
\instr{F5}{jump}{F6}{}
      {\annot{A3}{have}{B1}{have}{none}}

\\[0pt \color{mergec}]
\> @,@
\instr{F6}{pull sIn2 x2}{F7}{}
      {\annot{A0}{none}{B1}{have}{none}}

\\
\\[0pt \color{mergec}]
\> @,@
\icase{F7}{case (x1 < x2)}{F8}{}{F16}{}
      {\annot{A0}{none}{C0}{have}{have}}

\\
\\[0pt \color{mergec}]
\> @,@
\instr{F8}{push sOut2 x1}{F9}{}
      {\annot{A0}{none}{D0}{have}{have}}

\\[0pt \color{mergec}]
\> @,@
\instr{F9}{drop sIn1}{F10}{}
      {\annot{A0}{none}{D1}{none}{have}}

\\[0pt \color{sharec}]
\> @,@
\instr{F10}{pull sIn1 b1}{F11}{}
      {\annot{A0}{none}{D2}{none}{have}}

\\[0pt \color{groupc}]
\> @,@
\instr{F11}{jump}{F12}{v = b1}
      {\annot{A0}{pending}{D2}{pending}{have}}

\\[0pt \color{mergec}]
\> @,@
\instr{F12}{jump}{F13}{x1 = b1}
      {\annot{A1}{have}{D2}{pending}{have}}

\\[0pt \color{groupc}]
\> @,@
\icase{F13}{case (f || (l /= v))}{F14}{}{F15}{}
      {\annot{A1}{have}{C0}{have}{have}}

\\[0pt \color{groupc}]
\> @,@
\instr{F14}{push sOut1 v}{F15}{l = v, f = F}
      {\annot{A2}{have}{C0}{have}{have}}

\\[0pt \color{groupc}]
\> @,@
\instr{F15}{jump}{F7}{}
      {\annot{A3}{have}{C0}{have}{have}}

\\

\\[0pt \color{mergec}]
\> @,@
\instr{F16}{push sOut2 x2}{F17}{}
      {\annot{A0}{none}{E0}{have}{have}}

\\[0pt \color{mergec}]
\> @,@
\instr{F17}{drop sIn2}{F18}{}
      {\annot{A0}{none}{E1}{have}{have}}

\\[0pt \color{mergec}]
\> @,@
\instr{F18}{pull sIn2}{F7}{}
      {\annot{A0}{none}{E2}{have}{none}}

\\[0pt \color{black}]
@} }@
\end{tabbing}
